\bf Calendar-based graphics for visualizing people's daily schedules

### 2018-10-14 main.Rmd
added smart meter

The remainder of the paper is organized as follows. Section \ref{sec:algorithm} demonstrates the construction of the calendar layout in depth. Section \ref{sec:opt} lists and describes the options that come with the `frame_calendar` function. Section \ref{sec:examples} presents some variations of its usage. Section \ref{sec:discussion} discusses the advantages and disadvantages of the method.

@@

```{r flinders-2016, fig.height = 6.5, fig.cap = "The calendar-based display of hourly foot traffic at Flinders Street Station using line glyphs. The arrangement of the data into a 3 by 4 monthly grid represents all the traffic in 2016. The disparities between week day and weekend along with public holiday are immediately apparent."}
```

@@

# Variations
\label{sec:examples}

@@

```{r facet, fig.height = 11, fig.cap = "Line charts, embedded in the 6 by 2 monthly calendar, colored and faceted by the 3 sensors. The variations of an individual sensor are emphasised, and the shapes can be compared across the cells and sensors."}
```

@@

>>>>

The remainder of the paper is organized as follows. Section \ref{sec:algorithm} demonstrates the construction of the calendar layout in depth. Section \ref{sec:opt} lists and describes the options that come with the `frame_calendar` function. Section \ref{sec:variations} presents some variations of its usage. Section \ref{sec:discussion} discusses the advantages and disadvantages of the method.

@@

```{r flinders-2016, fig.height = 6.5, fig.cap = "The calendar-based display of hourly foot traffic at Flinders Street Station using line glyphs. The arrangement of the data into a $3 \\times 4$ monthly grid represents all the traffic in 2016. The disparities between week day and weekend along with public holiday are immediately apparent."}
```

@@

# Variations
\label{sec:variations}

@@

```{r facet, fig.height = 11, fig.cap = "Line charts, embedded in the $6 \\times 2$ monthly calendar, colored and faceted by the 3 sensors. The variations of an individual sensor are emphasised, and the shapes can be compared across the cells and sensors."}
```

@@

# Case study
\label{sec:case}

```{r load-elec, cache.extra = tools::md5sum("data/elec.rds")}
```

The case study uses individual-level energy usage from Australia. The dataset contains half-hourly electricity consumption data of 4 households over different time periods, with `r format(NROW(elec), big.mark = ",")` observations and `r NCOL(elec)` variables. The goal is to sketch typical profiles as well as unusual patterns in order to better understand each household's daily schedules.

Firstly, a letter value plot (ref??) shown as Figure \ref{fig:dow} helps grasp an overview of the variability between households across days of week. Household 2 has seen a great deal of variability in daily energy consumption, depicting relatively large variations on Thursdays. By contrast, household 4 consumes much less energy with constant variations. The dark blue line (representing median) highlights more energy consumed by households 1, 2, and 4 over the weekends relative to weekdays.

```{r dow, fig.height = 7, fig.cap = "Letter value plot of daily energy usage against day of week by households. The enery consumed by household 2 exhibits much larger variability, cotrast to the rest households. Households 1, 2, and 4 use mose energy over the weekends."}
```

```{r hod, fig.height = 6, fig.cap = ""}
```

```{r household23, fig.height = 11, fig.cap = ""}
```

### 2018-10-14 main.tex
added smart meter

The remainder of the paper is organized as follows. Section
\ref{sec:algorithm} demonstrates the construction of the calendar layout
in depth. Section \ref{sec:opt} lists and describes the options that
come with the \texttt{frame\_calendar} function. Section
\ref{sec:examples} presents some variations of its usage. Section
\ref{sec:discussion} discusses the advantages and disadvantages of the
method.

@@

\caption{The calendar-based display of hourly foot traffic at Flinders Street Station using line glyphs. The arrangement of the data into a 3 by 4 monthly grid represents all the traffic in 2016. The disparities between week day and weekend along with public holiday are immediately apparent.}\label{fig:flinders-2016}
\end{figure}

@@

\label{sec:examples}

@@

\caption{Line charts, embedded in the 6 by 2 monthly calendar, colored and faceted by the 3 sensors. The variations of an individual sensor are emphasised, and the shapes can be compared across the cells and sensors.}\label{fig:facet}
\end{figure}

@@

>>>>

The remainder of the paper is organized as follows. Section
\ref{sec:algorithm} demonstrates the construction of the calendar layout
in depth. Section \ref{sec:opt} lists and describes the options that
come with the \texttt{frame\_calendar} function. Section
\ref{sec:variations} presents some variations of its usage. Section
\ref{sec:discussion} discusses the advantages and disadvantages of the
method.

@@

\caption{The calendar-based display of hourly foot traffic at Flinders Street Station using line glyphs. The arrangement of the data into a $3 \times 4$ monthly grid represents all the traffic in 2016. The disparities between week day and weekend along with public holiday are immediately apparent.}\label{fig:flinders-2016}
\end{figure}

@@

\label{sec:variations}

@@

\caption{Line charts, embedded in the $6 \times 2$ monthly calendar, colored and faceted by the 3 sensors. The variations of an individual sensor are emphasised, and the shapes can be compared across the cells and sensors.}\label{fig:facet}
\end{figure}

@@

\hypertarget{case-study}{%
\section{Case study}\label{case-study}}

\label{sec:case}

The case study uses individual-level energy usage from Australia. The
dataset contains half-hourly electricity consumption data of 4
households over different time periods, with 64,128 observations and 5
variables. The goal is to sketch typical profiles as well as unusual
patterns in order to better understand each household's daily schedules.

Firstly, a letter value plot (ref??) shown as Figure \ref{fig:dow} helps
grasp an overview of the variability between households across days of
week. Household 2 has seen a great deal of variability in daily energy
consumption, depicting relatively large variations on Thursdays. By
contrast, household 4 consumes much less energy with constant
variations. The dark blue line (representing median) highlights more
energy consumed by households 1, 2, and 4 over the weekends relative to
weekdays.

{\centering \includegraphics[width=\textwidth]{figure/dow-1}

\caption{Letter value plot of daily energy usage against day of week by households. The enery consumed by household 2 exhibits much larger variability, cotrast to the rest households. Households 1, 2, and 4 use mose energy over the weekends.}\label{fig:dow}
\end{figure}

{\centering \includegraphics[width=\textwidth]{figure/hod-1}

\end{figure}

{\centering \includegraphics[width=\textwidth]{figure/household23-1}

\end{figure}
